---
title: "Synthpop workshop 1"
author: "David Henderson"
date: "15 June 2018"
output: 
  html_document:
    theme: spacelab
    toc: true
    toc_float: true
    code_folding: hide
    df_print: paged
---

```{r opts, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Pre-workshop prep

##Packages 

Load the package + others. I am using the `dplyr` package for data manipulation and the `skimr` package for summaries. If you don't have these packages installed then you can install them by typing e.g. `install.packages("dplyr")` 

```{r load_synthpop}
library(synthpop) #Must be loaded before tidyverse or dplyr::select is masked
library(dplyr)
library(magrittr)
library(skimr)
library(extrafont) # To 
```

##Look at the data

The `synthpop` package has a default dataset called `SD2011` automatically loaded for examples. Here I produce a summary of the data using the `skimr` package.

```{r data, results='asis'}
skim(SD2011) %>% skimr::kable()
```

This gives us a nice summary of the whole data frame.

For the purposes of the workshop we need to pick 4 variables from this that we will generate our first synthetic dataset from. 

##Pick my variables

I'm going to go for `sex`, `smoke`, `income` and `age`

Just for fun... `r anicon::faa("smile", animate = "bounce", size = 3)`


#Practical 1

##Task 1 My first two syntheses

The first task is to subset the dataframe using only these 4 variables. In the next chunk of code I declare an new object `test1` and then used the `dplyr` verb `select` to choose the 4 variables I mentioned above. I use `dplyr::glimpse()` to show this subset data frame in a tranposed format for ease of printing. 

```{r subset}
test1 <- 
  SD2011 %>% 
  select(c(sex, smoke, income, age))
test1
```

(need to fix histogram rendering - might be a `workflowr` problem??)

Potential probems for the synthesis? 

* `income` is not normally distributed
* The minimum value of `income` is negative ?? should be `NA`
* The level of missing data in `income` is almost 16%

Re render


## Add examples of different argument values. 


